TacticToe: Learning the Game of Tactics

### 2018-01-28 tactictoe_jv.tex
predictions: almost done

\subsection{Similarity}\label{sec:predictions}

We estimate the similarity (or co-distance) between two objects $o_1$ and $o_2$ 
through their respective feature sets $f_1$ and $f_2$.
%The similarity function $sim$ computed by the k-NN algorithm is analogous 
%to the one used in the premise selection task~\cite{ckju-pxtp13}.
The estimation is based on the frequency of the features in the intersection of 
$f_1$ and $f_2$. A good rule of thumb is that the rarer the shared features 
are, the more similar two goals should be. This can be realized by 
calculating TF-IDF weights for each feature~\cite{Jones72astatistical}.
We additionally raise the weights to the sixth power giving even more credence 
to rare features which was found experimentally optimal in \cite{cezary_cite}.

The first co-distance $sim_1$ adds a modified weight of each shared 
features to compute the total score.
In a second co-distance $sim_2$, we additionally take into account 
the total number of features to reduce the seemingly unfair advantage of big 
feature sets in the first scoring function.
\[sim_1 (o_1, o_2) = {\sum\nolimits_{\,f \in f_o \cap 
f_p}{\text{tfidf}(f)^{6}}}\]
\[sim_2 (o_1, o_2) = \frac{{\sum\nolimits_{\,f \in f_o \cap 
f_p}{\text{tfidf}(f)^{6}}}}
{ln (e + card(f_o) + card(f_p))}\]

>>>>

\subsection{Similarity}\label{sec:predictions}
We estimate the similarity (or co-distance) between two objects $o_1$ and $o_2$ 
through their respective feature sets $f_1$ and $f_2$.
%The similarity function $sim$ computed by the k-NN algorithm is analogous 
%to the one used in the premise selection task~\cite{ckju-pxtp13}.
The estimation is based on the frequency of the features in the intersection of 
$f_1$ and $f_2$. A good rule of thumb is that the rarer the shared features 
are, the more similar two goals should be. This can be realized by 
calculating TF-IDF weights for each feature~\cite{Jones72astatistical}.
We additionally raise the weights to the sixth power giving even more credence 
to rare features which was found experimentally optimal in \cite{}.\todo{CK: 
citation}

The first co-distance $sim_1$ adds a modified weight of each shared 
features to compute the total score.
In a second co-distance $sim_2$, we additionally take into account 
the total number of features to reduce the seemingly unfair advantage of big 
feature sets in the first scoring function.
\[sim_1 (o_1, o_2) = {\sum\nolimits_{\,f \in f_0 \cap 
f_1}{\text{tfidf}(f)^{6}}}\]
\[sim_2 (o_1, o_2) = \frac{{\sum\nolimits_{\,f \in f_0 \cap 
f_1}{\text{tfidf}(f)^{6}}}}
{ln (e + card(f_0) + card(f_1))}\]
